Software Citation Principles

### 2016-03-01 sc-principles/software-citation-principles.tex
Minor corrections

If certain metadata are not available, alternates may be provided:
\begin{itemize}
\item version number and release date: download date
\item location\slash respository: contact name\slash email if not publicly available
\end{itemize}

@@

Perhaps in recognition of the broad range of research domains struggling with the challenge of better recognizing the role of sofware, a number of community efforts hosted (and sponsored) by funders and agencies in both the US (NSF, NIH, Alfred P Sloan Foundation) and UK (SFTC, JISC) have run a number of workshops with participants from across a range of disciplines.

@@

One approach to increasing the `citability' of software is to encourage the submission of papers in standard journals describing a piece of research software. While some journals (e.g. F1000Research) have traditionally accepted software submissions, the American Astronomical Society (AAS) have recently annouced they will accept software papers in their journals \cite{aas-sofware-papers}.

>>>>

If certain metadata are not available, alternates may be provided:
\begin{itemize}
\item version number and release date: download date
\item location\slash repository: contact name\slash email if not publicly
  available
\end{itemize}

@@

Perhaps in recognition of the broad range of research domains struggling with
the challenge of better recognizing the role of software, a number of community
efforts hosted (and sponsored) by funders and agencies in both the US (NSF,
NIH, Alfred P Sloan Foundation) and UK (SFTC, JISC) have run a number of
workshops with participants from across a range of disciplines.

@@

One approach to increasing the `citability' of software is to encourage the
submission of papers in standard journals describing a piece of research
software. While some journals (e.g. F1000Research) have traditionally accepted
software submissions, the American Astronomical Society (AAS) have recently
announced they will accept software papers in their journals
\cite{aas-sofware-papers}.
